Notes on Perturbational Quantities

### 2008-08-06 docs/pert_notes/paper.tex
removed marginpars

{\bf What the code is currently doing:}\MarginPar{Do we need to change this?}

@@

{\bf What I'd like to do:}  Define $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  and 
$(\rho h)' = (\rho h)^{(1)}-(\rho h)_0^{(1)}$.  Then we predict $(\rho h)'$ to 

@@

{\bf What the code is currently doing:}\MarginPar{Do we need to change this?}

@@

{\bf What we would do to be consistent with density:} We would like to update the 

>>>>

{\bf What the code did before 8/6/08:}

@@

{\bf What the code currently does:}  Define $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  
and $(\rho h)' = (\rho h)^{(1)}-(\rho h)_0^{(1)}$.  Then we predict $(\rho h)'$ to 

@@

{\bf What the did before 8/6/08:}

@@

{\bf What the code does now:} We would like to update the 
